Structured Versus Decorated Cospans

### 2022-03-21 ResponseToReviews.tex

\iffalse
{\john He thought we were being dismissive because he didn't know that the ``tricks'' were all things I'd done myself!  If he looked at [1, Section 5] 
he'd see it was me coming up with a bunch of tricks to try to save the decorated cospan category of open graphs, and then Kenny and me explaining why 
this tricks don't work.  So maybe I should just delete ``despite all the tricks one might try''.  Sound good?}

{\chris Sounds good to me! See above, amend at will.}

{\kenny Sounds good.}
\fi

\item p. 3: ``Many of the flawed applications of decorated cospans have been fixed using structured cospans.” This dismisses the work of other 
scholars 
using the decorated cospan approach as flawed. The alleged flaw should be made more precise. What about the decorated cospan approach is inferior to 
the structured cospan approach?''
%The goal of this paper should be to illustrate to an applied category theory audience the differences between 
%decorated and structured cospans. Referring back to previous work of the authors to make that point does not provide value.

{\bf  The flaws---mathematical errors that render a number of claimed theorems incorrect---are now briefly explained in  in the Introduction, in the 
paragraph beginning ``Unfortunately, many applications of decorated cospans were flawed.''  In reference [3], Kenny Courser and John Baez analyzed 
these errors in detail and fixed them using structured cospans.  }

@@

\begin{enumerate}

\item p. 2. ``Unfortunately, many applications of decorated cospans were flawed… for reasons painstakingly explained in [1].''

Since fixing these problems is a major motivation for the whole paper, it would be good to explain what they are in slightly more detail, rather than 
just giving a reference. This could be done in a one paragraph or less. The gist of it, as I recall, is that in the original approach to decorated 
cospans, the isomorphism classes of open graphs depend on the identities of the edge elements, which is clearly wrong.

{\bf We have rewritten this paragraph to explain those flaws.  See also comment (6) in the second review.}

### 2022-03-21 cospans_new.tex
small fixes - perhaps we're done

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/03/20 - dealing with referee's comments

@@

Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor 
$\phi \maps \C \to \D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{\D} \to \widehat{\C}$ between presheaf 
categories which has a left adjoint $L \maps \widehat{\C} \to \widehat{\D}$.   Since presheaf categories have all small colimits and $L$ preserves them, 
the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, 
${}_L\lCsp(\widehat{\D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to 
show that ${}_L\lCsp(\widehat{\D})$ is a decorated cospan double category.  A simple example where $R$ is not an opfibration was 
provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the 
terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism
$(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.   It will be interesting to find conditions on $\phi \maps \C \to \D$ that 
guarantee ${}_L\lCsp(\widehat{\D})$ is isomorphic to a decorated cospan category, using the above machinery.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/03/21 - dealing with referee's comments

@@

Finally, it is worth mentioning a structured cospan double category to which the argument sketched above does \emph{not} apply.   For any functor $\phi \maps \C \to \D$ between small categories, precomposition with $\phi$ gives a functor $R \maps \widehat{\D} \to \widehat{\C}$ between presheaf categories which has a left adjoint $L \maps \widehat{\C} \to \widehat{\D}$.   Since presheaf categories have all small colimits and $L$ preserves them, the conditions of \cref{thm:structured_cospans} apply and we obtain a symmetric monoidal double category of structured cospans, ${}_L\lCsp(\widehat{\D})$.  However, the right adjoint $R$ is not always an opfibration---and when it is not, the above arguments cannot be used to show that ${}_L\lCsp(\widehat{\D})$ is a decorated cospan double category.  A simple example where $R$ is not an opfibration was  provided to us by Morgan Rogers.  Take $\phi \maps \mathsf{1} + \mathsf{1} \to \mathsf{1}$ to be the unique functor where $\mathsf{1}$ is the terminal category.  Then $R \maps \Set \to \Set^2$ is the diagonal, and the morphism $(0,0) \to (0,1)$ in $\Set^2$ admits no lift at all to $0 \in \Set$.   It will be interesting to find conditions on $\phi \maps \C \to \D$ that 
guarantee ${}_L\lCsp(\widehat{\D})$ is isomorphic to a decorated double cospan category.
